Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Add ref to appendix

%%%% Describe the problem.
\begin{itemize}
    \item ref to appendix
\end{itemize}

Haskell~\cite{haskell} has a strong type system, which ensures that most type errors are
detected at compile time rather than runtime.  Thanks to this, we assume that
programs written in Haskell have less bugs than programs written in programming
languages that do not provide such a strong type system.

@@

\subsection{Applying BDD to Haskell: An Example}
\label{sec:bcp-example}
This section shows how behavior driven development works in practice,
by means of the Fibonacci function.  Of course this is a very simple
example, but the method is also applicable to more sophisticated
situations where design decisions might not be as obvious as here.

We present a step-by-step refinement of a library, and a corresponding
spec.  Each line of code is only given once when introduced,
subsequent code fragments are incremental updates.

>>>>

%%%% Describe the problem.
Haskell~\cite{haskell} has a strong type system, which ensures that most type errors are
detected at compile time rather than runtime.  Thanks to this, we assume that
programs written in Haskell have less bugs than programs written in programming
languages that do not provide such a strong type system.

@@

\subsection{Applying BDD to Haskell: An Example}
\label{sec:bcp-example}
This section shows how behavior driven development works in practice,
by means of the Fibonacci function.  This is a very simple
example, but the method is also applicable to more sophisticated
situations where design decisions might not be as obvious as here.

We present a step-by-step refinement of a library, and a corresponding
spec.  Each line of code is only given once when introduced,
subsequent code fragments are incremental updates.  Appendix
\ref{sec:appendix-code} contains the complete code of this section.
